Nitrogen cycling in the CLM5: controls on responses to environmental forcing

### 2018-11-06 main.tex

\section{Results}

The analysis conducted involved 6 sites, with 13 parameters perturbed to 4 different values, the each of those with an increase CO2, N and control run. Including the default simulations, this is 936 different run configurations. In this analysis, we look at the parameteric responses of five chosen output variables (GPP, NPP, LAI, Leaf N and vegetation carbon) first for their impacts on the system state and then on the responses to carbon and nitrogen limitation.

>>>>

\section{Results}
The analysis conducted involved 6 sites, with 13 parameters perturbed to 4 different values, the each of those with an increase CO2, N and control run. Including the default simulations, this is 936 different run configurations. In this analysis, we look at the parameteric responses of five chosen output variables (GPP, NPP, LAI, Leaf N and vegetation carbon) first for their impacts on the system state and then on the responses to carbon and nitrogen limitation.
